Appendix for 'Framing Effects in the Wild

### 2022-09-19 paper/appendix.Rmd
Rewrite structure

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center')

@@

# Frames in Communication

@@

### Migration

### Crime

@@

## Correcting for change in DPA-sourced content

@@

@@

# Readership models

## Inward selection

```{r inselection, fig.cap="Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change."}

```
## Crowding out

# Difference-in-Differences Estimates

@@

## Descriptives

Show Demographics for Treatment and Control Groups.

@@

## DiD assumptions

### Parallel Trends

@@

@@

## Variable: Immigration Attitudes

### Outcome: Reduce Immigration (1130)

#### Treatment groups across time

(add counterfactual if time)

```{r did_imm_att_plot}

fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(!is.na(`1130_clean`), !is.na(treat)) %>% 
  group_by(treat, wave) %>% 
  summarise(
    date_clean = min(date_clean, na.rm = T),
    mig_mean = mean(`1130_clean`, na.rm = T),
    mig_sd = sd(`1130_clean`, na.rm = T),
    N = n()
  ) %>% 
  mutate(
    mig_lower = mig_mean + qt(0.025, df = N-1) * (mig_sd/sqrt(N)),
    mig_upper = mig_mean + qt(0.975, df = N-1) * (mig_sd/sqrt(N))
  ) %>% 
  ggplot(aes(x = date_clean, y = mig_mean,
             ymin = mig_lower, ymax = mig_upper,
             lty = !treat, col = !treat)) +
  geom_line() +
  geom_pointrange() +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
  theme_minimal() +
  labs( x = "", y = "", col = "Readership", lty = "Readership") +
  scale_color_manual(labels = c("Bild", "Never Bild"),
                     values = MetBrewer::met.brewer("Archambault", 2)) +
  scale_linetype_manual(labels = c("Bild", "Never Bild"),
                     values = c(1,2))

#### Effect of Reichelt takeover

```{r did_imm_att}

### Outcome: Integration Attitude (1210)

#### Effect of Reichelt takover

```{r did_int_att}

SingleDVModel("1210_clean")

## Variable: Voting Behaviour

### Outcome: Scalometer AfD (430i)

#### QUESTION TEXT MISSING

#### DiD Estimate

```{r afd_scale}

SingleDVModel("430i_clean")

## Variable: Issue Importance

### Outcome: MIP Migration (840s)

#### QUESTION TEXT MISSING

#### DiD Estimate

```{r did_mip_mig}

SingleDVModel("mip_mig")

## Variable: Crime Considerations

### Attitudes towards fighting crime (2880h)

#### Direct Effect

```{r did_crime_att}

SingleDVModel("2880h_clean")

#### Bootstrap of correlations

```{r crime_mig_cor}

cors <- 
  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(!is.na(`1130_clean`), !is.na(`2880h_clean`), !is.na(treat)) %>% 
  group_by(treat, post) %>% 
  summarise(mig_crime_cor = cor(`1130_clean`, `2880h_clean`, use = "complete.obs")) %>% 
  mutate(universe = "factual")

cors <- 
  cors %>% 
  rbind(
    data.frame(
      treat = c(TRUE, TRUE),
      post = c(FALSE, TRUE),
      mig_crime_cor = c(cors[cors$treat & !cors$post, "mig_crime_cor"][[1]], 
                        cors[cors$treat & !cors$post, "mig_crime_cor"][[1]] +  
                          sqrt((cors[cors$treat & cors$post, "mig_crime_cor"][[1]] -
                          cors[!cors$treat & cors$post, "mig_crime_cor"][[1]])^2)),
      universe = "counterfactual"
    ), 
  ) %>% 
  mutate(universe = factor(universe, levels = c("factual", "counterfactual")))

cors %>% 
  mutate(treat_universe = paste(treat, universe, sep = "_")) %>% 
  ggplot(aes(x = post, y = mig_crime_cor, col = treat, lty = universe, group = treat_universe)) +
  geom_point() +
  geom_line() +
  theme_minimal()

#### Interaction of DiD with Crime Attitude (following Nelson & Kinder 1996)

@@

>>>>

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', fig.pos = "!ht", out.extra = "")

@@

# Variables & Decriptives

## Dependent Variables

### Overview

Table, treated vs. untreated

### Immigration Attitudes (1130 in GLES)

*Translated:*

Now it's about immigration opportunities for foreigners. Should immigration opportunities for foreigners be made easier or restricted?

(1) Make it easier for foreigners to move here
(2)
(3)
(4)
(5)
(6)
(7) Restrict immigration of foreigners

---

*Original/DE:*

#### Distribution

```{r}

GroupedDistPlot()

### Integration Attitudes (1210 in GLES)

*Translated:*

There are different opinions about how much foreigners in Germany should adapt. Some think that foreigners should fully assimilate to German culture. Others think that foreigners should be able to live according to their own culture if possible.

(1) Foreigners should fully assimilate to German culture
(2)
(3)
(4)
(5)
(6)
(7) Foreigners should, if possible, be able to live according to their own culture

---

*Original/DE:*

### MIP: Immigration (840 in GLES)

*Translated:*

In your opinion, what is the most important political problem in Germany at the moment?
Please name only one *single* problem.

*0/1 indicator assessing mention of any migration related code (3411-3413 or 3750-3759; find coding scheme on GLES website).*

---

*Original/DE:*

Was ist Ihrer Meinung nach gegenwärtig das wichtigste politische Problem in Deutschland? 
Hinweistext: Nennen Sie bitte nur ein *einziges* Problem.

### AfD Scalometer

*Translated:*

What do you think of the individual political parties in general? AfD (Alternative for Germany)

(1) -5 don't think much of the party at all
(2) -4
(3) -3
(4) -2
(5) -1
(6) 0
(7) +1
(8) +2
(9) +3
(10) +4
(11) +5 think very highly of the party

(-71) I don't know [labeled as "not known" in the data set]

*Recoded to [-5, 5].*

---

*Original/DE:*

Was halten Sie so ganz allgemein von den einzelnen politischen Parteien? AfD (Alternative für Deutschland)

(1) -5 halte überhaupt nichts von der Partei 
(2) -4 
(3) -3 
(4) -2 
(5) -1 
(6) 0 
(7) +1 
(8) +2 
(9) +3 
(10) +4 
(11) +5 halte sehr viel von der Partei

(-71) kenne ich nicht [im Datensatz gelabelt als „nicht bekannt“]

### Attitude towards fighting crime (2880h)

*Translated:*

State powers to fight crime should be expanded, even if this means more surveillance of citizens.

(1) totally disagree
(2) rather disagree
(3) partly/partly
(4) tend to agree
(5) I totally agree

*Recoded to [-2, 2].*

---

*Original/DE:*

## Bild Readership

## Media Exposure Variables

### Other Newspapers

### TV News

### Internet News Consumption

# Treatment

@@

### Dictionaries

### Handcoding

### Preprocessing

### Training

@@

### Correcting for change in DPA-sourced content

@@

### Raw Crime Estimates

@@

### Migration Attention over Time

# Results

## Treatment Groups

@@

@@

## Parallel Trends

@@

## Robustness of Main Effect

```{r did_imm_att, results='asis'}

## Multiple DV Table

## Longterm-Panel Model

@@

## Association Model

@@

## Readership models

### Inward selection

```{r inselection}

Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change.

### Crowding out
